The value of intermediation

### 2022-09-15 src/presentation/presentation.qmd
Switch to mathjax 3 for better output

---
title: "The value of intermediation"
author: "Martin Stancsics"
format:
    revealjs:
        embed-resources: true
        transition: fade
        toc: true
        toc-depth: 1
        toc-title: Agenda
bibliography: references.bib
---

>>>>

---
title: "The value of intermediation"
author: "Martin Stancsics"
format:
    revealjs:
        embed-resources: true
        html-math-method: mathjax
        transition: fade
        toc: true
        toc-depth: 1
        toc-title: Agenda
bibliography: references.bib
---
